Analyzing MLG distribution

### 2017-04-11 doc/RMD/MLG-distribution.Rmd
update to save graphs
update name of data

---
title: "R Notebook"
output: 
  html_notebook:
    toc: true
---

@@

```{r}
load("data/sclerotinia_16_loci.dat")
setPop(dat) <- ~Region
dat
locNames(dat)
other(dat)$REPLEN
head(other(dat)$meta)
keeploci <- !locNames(dat) %in% colnames(corrected_loci)
dat11 <- dat[loc = keeploci, mlg.reset = TRUE] # reducing to 11 loci and recalculating mlgs
dat11
```

@@

>>>>

---
title: "Analyzing MLG distribution"
output: 
  html_notebook:
    toc: true
---

@@

```{r}
load("data/sclerotinia_16_loci.rda")
setPop(dat) <- ~Region
dat
locNames(dat)
other(dat)$REPLEN
head(other(dat)$meta)
keeploci <- !locNames(dat) %in% colnames(corrected_loci)
dat11 <- dat[loc = keeploci, mlg.reset = TRUE] # reducing to 11 loci and recalculating mlgs
dat11
```

@@

```{r, saving_data}
save(graph16loc, graph11loc, alt_layout, file = "data/mlg-crosspop-graph.rda")
```
